Summary Tables

### 2021-10-26 summary_tables.Rmd
Regen all outputs for latam cities

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']

#cities <- c('accra','sao_paulo','buenos_aires')

>>>>

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- TRUE
#cities <- c('accra','sao_paulo','buenos_aires')
